On Secure Delegation of SampBQP with a Classical Client

### 2020-01-18 qpip0.tex
Realize the need to generalize parallelrep

\begin{lem}
	Let $m=O(\log n)$ \Ethan{$n$ is problem size?}, $\gamma_0\in[0, 1]$, and $T\in\bbN$ such that $\frac{\gamma_0}{T}=\frac{1}{\poly(n)}$.
	Let $\gamma_i\xleftarrow{\$}\set{\frac{j\gamma_0}{T}}^T_{j=1}$ \Ethan{This is a set, right? Doesn't look like one in the original document} for each $i\in[m]$.
	Then a state $\ket{psi}_{X, Z}$ can be partitioned as follows: \Ethan{Just gonna hard-code $c=0^m$ here for now}
	$$\ket{\psi}=TODO$$
	where the way of partitioning may depend on the choices of $\hat\gamma=(\gamma_i)_{i=1}^m$.
	Furthermore, the following properties are satisfied.
	\begin{enumerate}
		\item stuff
		\item stuff
		\item stuff
		\item stuff
		\item stuff
	\end{enumerate}
\end{lem}

>>>>

\begin{lem}
	Let $m=O(\log n)$ \Ethan{$n$ is problem size?}, $\gamma_0\in[0, 1]$, and $T\in\bbN$ such that $\frac{\gamma_0}{T}=\frac{1}{\poly(n)}$.
	Let $\gamma_i\xleftarrow{\$}\set{\frac{j\gamma_0}{T}}^T_{j=1}$ \Ethan{This is a set, right? Doesn't look like one in the original document} for each $i\in[m]$.
	Then a state $\ket{psi}_{X, Z}$ can be partitioned as follows: \Ethan{Just gonna hard-code $c=0^m$ here for now}
	$$\ket{\psi}=\ket{\psi_0}+\ket{\psi_{10}}+\ket{\psi_{110}}+\ldots+\ket{\psi_{11\ldots10}}+\ket{\psi_{11\ldots11}}+\ket{\psi_{err}}$$
	where the way of partitioning may depend on the choices of $\hat\gamma=(\gamma_i)_{i=1}^m$.
	Furthermore, the following properties are satisfied. \Ethan{Takes a bit of parsing to see how is our case different here since $c$ might be defined differently for us}
	\begin{enumerate}
		\item stuff
		\item For any fixed $\hat\gamma$... 
		\item For any fixed $\hat\gamma$...
		\item For any fixed $c$,
			$$\E_{\hat\gamma}\left[\norm{\ket{\psi_{err}}_{X,Z}}^2\right]\leq\frac{6m^2}{T}+\negl(n)$$
		\item stuff
	\end{enumerate}
\end{lem}
